---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# klct

<!-- badges: start -->
<!-- badges: end -->

This package contains functions to read in and analyze microCT data from a
NeoScan scanner as currently performed in the Khosla Lab. Sites analyzed include
femoral metaphysis, femoral diaphysis, and lumbar vertebra. Analyses include
trabecular bone parameters and cortical bone parameters.

Both parametric (*t*-test, two-way ANOVA) and nonparametric (Wilcoxon rank-sum,
Aligned Rank Transform via `ARTool`) tests are supported. Comparisons can be
made between two treatments (with each sex analyzed separately), or between two
treatments and two sexes in a full two-way design.

Measures are detected dynamically from the data, and the `measures` parameter
lets you analyze sensible defaults (`NULL`), all detected columns (`"all"`), or
a custom set of column names.

Mayo-themed R Markdown templates are available via the
[mayodown](https://github.com/KhoslaLab/mayodown) package.

## Installation

You can install the development version of klct from
[GitHub](https://github.com/KhoslaLab/klct) with:

``` r
# install.packages("remotes")
remotes::install_github("KhoslaLab/klct")
```

## Example

```{r example}
library(klct)

mouse_table <- read_mouse_table(klct_ex("mouse-table.csv"))

spine_trab <- read_trabecular(klct_ex("spine_trabecular_data.csv"),
                              mouse_table, site = "Spine")

# Parametric comparison (default)
Spine.Tb <- compare_groups(spine_trab)

# Nonparametric comparison
Spine.Tb_np <- compare_groups(spine_trab, test = "nonparametric")

# All available trabecular measures
Spine.Tb_all <- compare_groups(spine_trab, measures = "all")

# Two-way (Treatment x Sex) comparison
Spine.Tb_2x2 <- compare_groups_2x2(spine_trab)
```

```{r print, results = "asis"}
print_results(Spine.Tb)
```

## Templates

Four R Markdown templates are available from the RStudio template menu
(`File > New File > R Markdown > From Template`), via RStudio Addins
(`Addins > klct`) or via helper functions:

```r
# Standard templates
create_two_treatment_comparison()
create_two_treatment_two_sex_comparison()

# Mayo-themed templates (uses mayodown::mayohtml)
create_two_treatment_comparison(mayo = TRUE)
create_two_treatment_two_sex_comparison(mayo = TRUE)
```

Parametric and nonparametric results are displayed as separate tabs within each
section, and Combined Sexes Plots tabs are included in all sections.
